%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager, DevOps} % Job title
    {Suncor} % Organization
    {Mississauga, Ontario} % Location
    {June 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provisioned an easily managable hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Ansible, Packer and Terraform.}
        \item {Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.}
        \item {Designed an overall service architecture and pipelines of the Machine Learning based Fashion Tagging API SaaS product with the micro-services architecture.}
        \item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.}
        \item {Deployed a centralized logging environment(ELK, Filebeat, CloudWatch, S3) which gather log data from docker containers and AWS resources.}
        \item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Manager, Quality Management} % Job title
    {Suncor} % Organization
    {Mississauga, Ontario} % Location
    {May 2019 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).}
        \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Management Specialist - Downstream \& Technical Testing} % Job title
    {Suncor} % Organization
    {Mississauga, Ontario} % Location
    {Oct 2015 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
        \item {Implemented a distributed web stress test tool with high anonymity.}
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Management Test Coordinator} % Job title
    {Suncor} % Organization
    {Mississauga, Ontario} % Location
    {July 2011 - Sept 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
        \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
        \item {Won the 2nd prize in final evaluation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fraud Test Consultant (Contract)} % Job title
    {CIBC - Remote Banking and Shared Services} % Organization
    {Toronto, Ontario} % Location
    {Feb 2010 - July 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
        \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Visa Debit: UAT Test Manager (Contract)} % Job title
    {CIBC Retail Markets} % Organization
    {Toronto, Ontario} % Location
    {Feb 2009 – Jan 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for managing the User Acceptance Test (UAT) across multiple business groups as part of the launch of the first VISA Debit product into the Canadian marketplace}
        \item {Coordinated program testing across tests for card issuance, point-of-sale transactions, settlement and reconciliation, disputes \& charge backs and loyalty program enrollment \& fulfillment}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Test Consultant (Contract)} % Job title
    {Accenture} % Organization
    {Toronto, Ontario} % Location
    {Nov 2008 - Dec 2008} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Financial Services Consultant} % Job title
    {Accenture} % Organization
    {Toronto, Ontario} % Location
    {Sept 2003 – Oct 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {PROJECT MANAGER - Coordinated program testing across tests for card issuance, point-of-sale transactions, settlement and reconciliation, disputes \& charge backs and loyalty program enrollment \& fulfillment}
        \item {DEVELOPMENT LEAD - Coordinated program testing across tests for card issuance, point-of-sale transactions, settlement and reconciliation, disputes \& charge backs and loyalty program enrollment \& fulfillment}
        \item {BUSINESS ANALYST - Coordinated program testing across tests for card issuance, point-of-sale transactions, settlement and reconciliation, disputes \& charge backs and loyalty program enrollment \& fulfillment}
        \item {TEST LEAD - Coordinated program testing across tests for card issuance, point-of-sale transactions, settlement and reconciliation, disputes \& charge backs and loyalty program enrollment \& fulfillment}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-op Internships} % Job title
    {Additional Experience} % Organization
    {Various} % Location
    {1997 - 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Marketing and technology roles at Microsoft Canada, Bell Canada, Cisco Systems, Dofasco, Delano Technology Corp, and Aird \& Berlis LLP}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
